Reanalysis Step 4: Main Effects Outcome Analysis

### 2025-08-27 reanalysis-4-outcome_analysis.qmd
contrasts

# Set other variables to their weighted means/modes
weighted_means <- svydesign(ids = ~1, weights = ~weights, data = imp_data) |>
  svymean(~baseline_VA_logMAR + age + CCI + DCSI, na.rm = TRUE)

>>>>

# Set other variables to their weighted means/modes
design_temp <- svydesign(ids = ~1, weights = ~weights, data = imp_data)
weighted_means <- svymean(~baseline_VA_logMAR + CCI + DCSI, design_temp, na.rm = TRUE)
